Physics-Informed Neural ODEs (PINODE)

### 2023-05-16 presentation/phd_defense_pres.tex
Add CS plots

\begin{frame}{TODOs}
\end{frame}

@@

\begin{frame}{Single-Pixel Imaging}
1) Now we switch gears to show you an application to single-pixel imaging
2) It shows how powerful these differentiable reduced-order models can be in applications besides forecasting and motivate the need to improve those.
3) SPI setup is a single-pixel camera with mirror array… 
\end{frame}

\begin{frame}{Compressive Sensing with Reduced-Order Models}
	1) We introduce a ROM as a relaxation of a PDE-constrained compressive sensing.
	2) We search in the latent space of a ROM for the right trajectory that matches both the ROMs predictions and the compressive-sensing observations
\end{frame}

>>>>

@@

\begin{frame}{Single-Pixel Imaging}
%1) Now we switch gears to show you an application to single-pixel imaging
%2) It shows how powerful these differentiable reduced-order models can be in applications besides forecasting and motivate the need to improve those.
%3) SPI setup is a single-pixel camera with mirror array… 
\begin{figure}
	\includegraphics[width=\textwidth]{Figures/SPI_setup.pdf}
\end{figure}
\end{frame}

\begin{frame}{Single-Pixel Imaging}
	% This is how SPI setup translates into Math
	\includegraphics[width=\textwidth]{Figures/spi_math.png}
\end{frame}

\begin{frame}{Compressive Sensing with Reduced-Order Models}
	%1) We introduce a ROM as a relaxation of a PDE-constrained compressive sensing.
	%2) We search in the latent space of a ROM for the right trajectory that matches both the ROMs predictions and the compressive-sensing observations
	\includegraphics[width=\textwidth]{Figures/cs_schematics.png}
\end{frame}
